### 2022-01-20 R/Analyse zero catch advice.Rmd
UPdates several files

# -----------------------------------------------------------------------------------------------
# Analyse changes in pelagic stocks.Rmd
#
# 07/01/2019 first coding; adapted from ICES advice and assessment summaries.Rmd
# 10/01/2018 made small changes to the table
# 04/05/2019 updated for WKRRMAC 2019; focus on mackerel
# 06/06/2019 changed the data frame d; now also has purpose
# -----------------------------------------------------------------------------------------------

@@

  filter(grepl("her-47|mac-67|mac-nea|whb-c|whb-n|hom-c|hom-w|her-3a22|her-noss",
               stockkeylabelold)) %>%
  # filter(grepl("mac-67|mac-nea", 
  #              stockkeylabelold)) %>%

@@

  filter(assessmentyear >= 2008) %>% 
  ungroup()

@@

ass <-
  iAssess %>% 
  filter(stockkeylabelold %in% unique(adv$stockkeylabelold)) %>% 
  filter(assessmentyear %in% unique(adv$assessmentyear)) %>% 
  filter(year <  assessmentyear) %>% 
  filter(year >= 2000) %>%

@@

**Analysis of advice changes in a number of key pelagic stocks**

@@

@@

ass_5year %>%

@@

  geom_line(aes(size=purpose)) +
  geom_line(data=ass_final, aes(colour=purpose ), size=1.5) +
  # geom_dl(aes(label  = ayear, group=purpose), method = list(dl.combine("last.points"), cex = 0.8)) +

@@

  expand_limits(y=0) + 
  labs(y="SSB",y="") +
  facet_wrap(~stockkeylabelold, scales="free_y")

>>>>

# -----------------------------------------------------------------------------------------------
# Analyse zero catch advice.Rmd
#
# 26/02/2020 adapted from Analyse changes in pelagic stocks
# -----------------------------------------------------------------------------------------------

@@

  # filter(grepl("mac-67|mac-nea|whb-c|whb-n|her-noss|her-47d3",
  #              stockkeylabelold)) %>%
  # filter(grepl("her-47|mac-67|mac-nea|whb-c|whb-n|hom-c|hom-w|her-3a22|her-noss",
  #              stockkeylabelold)) %>%
  # filter(grepl("mac-67|mac-nea", 
  #              stockkeylabelold)) %>%

@@

  filter(assessmentyear >= 2000) %>% 
  ungroup()

@@

ass <-
  iAssess %>% 
  filter(stockkeylabelold %in% unique(adv$stockkeylabelold)) %>% 
  filter(assessmentyear %in% unique(adv$assessmentyear)) %>% 
  filter(year <=  assessmentyear) %>% 
  filter(year >= 2000) %>%

@@

**Analysis of zero catch advice**

@@

adv %>% 
  filter(purpose == "advice") %>% 
  filter(advisedlandingsmax == 0 | advisedcatchmax == 0) %>%  
  filter(tacyear <= 2018) %>% 
  filter(!is.na(tal)) %>% 
  dplyr::select(speciesfaocode, stockkeylabelold, assessmentyear, tacyear, advisedlandingsmax, tal, landings, catches) %>%
  ungroup() %>% 
  mutate(catch     = ifelse(!is.na(catches), catches, landings)) %>% 
  mutate(zerotac   = ifelse(tal   == 0, 1, 0)) %>% 
  mutate(zerocatch = ifelse(catch == 0, 1, 0)) %>% 
  # View()
  group_by(tacyear) %>% 
  summarize(nzeroadvice = n(),
            nzerotac    = sum(zerotac, na.rm=TRUE),
            nzerocatch  = sum(zerocatch, na.rm=TRUE)) %>% 
  gather(key="variable", value="data", nzeroadvice:nzerocatch) %>%

  geom_line(aes(y=data, group=variable, colour=factor(variable))) +
  geom_point(aes(y=data, group=variable, colour=factor(variable))) +

  scale_x_continuous(breaks=pretty_breaks()) +
  expand_limits(y=0) + 
  labs(y="N stocks") 
#  facet_wrap(~variable)

adv %>% 
  filter(purpose == "advice") %>% 
  filter(advisedlandingsmax == 0 | advisedcatchmax == 0) %>%  
  filter(tacyear <= 2018) %>% 
  filter(!is.na(tal)) %>% 
  dplyr::select(speciesfaocode, stockkeylabelold, stockkeylabelnew, assessmentyear, tacyear, advisedlandingsmax, tal, landings, catches) %>%
  ungroup() %>% 
  mutate(catch     = ifelse(!is.na(catches), catches, landings)) %>% 
  mutate(zerotac   = ifelse(tal   == 0, 1, 0)) %>% 
  mutate(zerocatch = ifelse(catch == 0, 1, 0)) %>%

  write.csv(file="zerocatch.csv", row.names = FALSE)

@@

my.stock <- c("whb-comb", "her-noss", "her-47d3", "mac-nea")
my.year  <- 2010:2019

# ass %>% 
ass_10year %>%

  filter(stockkeylabelold %in%  my.stock) %>% 
  filter(assessmentyear %in%  my.year) %>%

@@

  geom_line(aes(size=purpose)) +
  geom_line(data=subset(ass_final, 
                        stockkeylabelold %in% my.stock & assessmentyear %in% my.year), 
            aes(colour=purpose ), size=1.5) +
  # geom_dl(aes(label  = ayear, group=purpose), method = list(dl.combine("last.points"), cex = 0.8)) +

@@

  expand_limits(y=0) + 
  labs(y="SSB",y="") +
  facet_wrap(~stockkeylabelold, scales="free_y")
  # facet_wrap(~assessmentyear, ncol=4)
